%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Thanks : Rishi Shah 's Contribution
% inspired by his awesome contribution:
% https://www.overleaf.com/articles/rishi-shahs-resume/vgxvkmxktyxn
% Author : Allianzcortex
% contact me : github.com/Allianzcortex
% email : iamwanghz#gmail.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}
% {\centerline }
% \end{center}
\name{Dr. Trevor Michael Tomesh} % Your name 


%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faGithub{ github.com/trevortomesh} \faLink{https://www.linkedin.com/in/trevortomesh/} \faEnvelope{trevor.tomesh@uregina.ca}}
\address{\faMapMarker{University of Regina, Regina SK, Canada} \faPhone(306)-550-2369} % Your address

\begin{document}
{\centerline {}}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Regina} \hfill {\em September 2013 - June 2020} 
\\{ \textit {PhD in Computer Science }} 

{\bf University of Wisconsin River Falls} \hfill {\em September 2006 - May 2011} 
\\ { \textit {BSc Physics}} \hfill \\ \\
\small Minor in Mathematics \smallskip \\
\small Member of Sigma Pi Sigma Physics Honors Society \\
\small Ronald E. McNair Scholar

\end{rSection}

\begin{rSection}{Relevant Coursework}
\emph{Graduate}
\begin{itemize}
    \item CS 839 - Web Intelligence and Electronic Commerce
    \item CS 827 - Computer Audio
    \item CS 805 - Computer Graphics
    \item CS 807 - Building Interactive Gadgets
    \item CS 809 - Interactive Software
    \item CS 805 - Human Computer Interactions
\end{itemize}

\emph{Undergraduate}
\begin{itemize}
    \item General Physics I \& II
    \item Modern Physics
    \item General/Intermediate Physics Laboratories
    \item Calculus I-III,
    \item Math For Physics and Engineering I \& II
    \item Discrete Math
    \item Scientific Programming
    \item Mathematical Programming
    \item Differential Equations
    \item Astronomy
    \item Electronics (circuits)
    \item Advanced Physics Laboratory
    \item Thermodynamics
    \item Classical Mechanics
    \item Astrophysics
    \item Electricity and Mag.
    \item Linear Algebra
    \item Quantum Mechanics
    \item Numerical Analysis
    \item Independent Study In Computational Physics
\end{itemize}

\end{rSection}

\begin{rSection}{Research}

\subsection*{General Research Interests}
\begin{itemize}
    \item Research Interests
    \item General Systems Theory
    \item Amalgamated Systems
    \item Complex Systems
    \item Analogous Systems
    \item Analog Computing Systems
    \item Constrained Resource Computing
    \item Embedded Computing
    \item Information Theory
    \item Open Source Hardware
    \item Simulation Methods
    \item Games Studies
    \item Literate Programming
\end{itemize}    

\subsection*{Research Assistant, IceCube Neutrino Detector - 2007}
UW-River Falls Physics Department, River Falls, Wisconsin 
\begin{itemize}
    \item Built temperature stabilizing sunshades for digital optical modules,
to be used at South Pole
    \item Constructed customized crates for materials to be shipped to
Antarctica
    \item Learned and used AutoCAD to digitally document cargo crate design.
\end{itemize}

\subsection*{Technical Assistant, UW River Falls Physics Department - 2006-2011}
UW River Falls Physics Department, River Falls, Wisconsin
\begin{itemize}
    \item Assisted in technical and manual departmental work.
    \item Built demonstrations for Society of Physics Students outreach activities.
    \item Repaired and maintained laboratory equipment.
    \item Set up laboratory equipment.
    \item Construct Digital Displays.
    \item Graded physics homework / Tutored students
\end{itemize}

\subsection*{Researcher, UW River Falls Radio Telescope - 2009}
UW River Falls Physics Department, River Falls, Wisconsin
\begin{itemize}
    \item Constructed a functional Radio JOVE radio telescope to "listen" to
            radio signals from Jupiter's magnetosphere.
    \item Processed, analyzed and visualized data.
\end{itemize}

\subsection*{Researcher, Research Experience for Undergraduates Program - 2009}
Vanderbilt University, Physics Department, Nashville, Tennessee
\begin{itemize}
    \item Computationally modeled the effects of black hole kicks on the
    density of globular clusters by running an Nbody simulation on the ACCRE
    supercomputing cluster.
    \item Was responsible for writing a density profiling program in FORTRAN to
    analyzed the density of a globular cluster on a logarithmic scale.
    \item Wrote scripts in supermongo to produce movies of the physical evolution
    and the density evolution of these globular clusters.
    \item Appended to N-body simulation a routine to provide random gravitational wave
    recoils to pairs of merging black holes.
\end{itemize}

\subsection*{Interim Research Assistant - 2010}
University of Worcester, Computing Department, Worcester, England
\begin{itemize}
    \item Designed and developed simulations in the fields of waves and
    oscillations using video game technology for physics education
    \item Used the Unreal Tournament 2004 engine to model oscillators
    realized and developed effective models for the K-12
    and undergraduate physics classrooms.
    \item Evaluated the fidelity of these models by comparing to theoretical and
    computational models.
\end{itemize}

\subsection*{Graduate Research in Educational Game Development - 2011-2012}
University of Worcester, Computing Department, Worcester, England
\begin{itemize}
    \item Developed a working prototype of an educational game targeted at high school physics students
    in the Blender Game Engine.
    \item Met with instructors to gather design specifications.
    \item Carried out student interviews to asses knowledge and experiences with educational 
    games and interest in games for learning.
    \item Presented research at various conferences in Europe and the UK. 
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching Experience}
\subsection*{Sessional Lecturer - University of Regina (2014 - Present)}
\emph{Courses Taught:}
\begin{itemize}
    \item CS 207 - Building Interactive Gadgets (2014 - Present)
    \item CS 427 / 827 - Computer Audio (Fall 2018)
    \item CS 330 - Intro to Operating Systems (Spring 2018)
    \item CS 290 AK - Topics in Data Acquisition and Analysis (Winter 2018)
    \item CS 290 AJ - Interactive Simulation Methods (Fall 2017, Winter 2019)
    \item CS 829 - Information Theory and Applications (Summer 2019, Summer 2020)
    \item CS 890AC - Data Analysis from the Internet (Summer 2019)
    \item CS 455 / 855 - Mobile Computing (Fall 2019)
    \item CS 490 DB - Topics in Natural Science (Fall 2019)
    \item CTCH 310 AD - "Intro to Computer Game and VR Design" (Winter 2018, Winter 2019)
 \end{itemize} 
\end{rSection}

\begin{rSection}{Publications}

Tomesh, T. and Hepting, D. (2017). Environmental sensing with recycled materials.
[online] O'Reilly Media. Available at: https://www.oreilly.com/ideas/environmentalsensing-with-recycled-materials [Accessed 27 Mar. 2019].

Tomesh, Trevor Michael, and Daryl H. Hepting. ``DIY game console development.''
Proceedings of the first ACM SIGCHI annual symposium on Computer-human
interaction in play. ACM, 2014.

Tomesh, Trevor M. ``Teaching programming with Python and the Blender Game
Engine.''

Tomesh, Trevor, and Colin Price. ``Design and development of physics simulations in
the field of oscillations and waves suitable for k-12 and undergraduate instruction
using video game technology.'' APS Meeting Abstracts. 2011.

Tomesh, Trevor. ``Computational Simulation of a Simple Pendulum Driven by a
Natural Chaotic Function.'' APS March Meeting Abstracts. 2010.
\end{rSection}

\begin{rSection}{Peer Review}

Mouhoub, Malek, et al., eds. Recent Trends and Future Technology in Applied
Intelligence: 31st International Conference on Industrial Engineering and Other
Applications of Applied Intelligent Systems, IEA/AIE 2018, Montreal, QC, Canada,
June 25-28, 2018, Proceedings. Vol. 10868. Springer, 2018.

Amine, Abdelmalek, et al., eds. Computational Intelligence and Its Applications: 6th
IFIP TC 5 International Conference, CIIA 2018, Oran, Algeria, May 8-10, 2018,
Proceedings. Vol. 522. Springer, 2018.
\end{rSection}
\end{document}
